Manuscript Figures for Genome Biology

### 2018-09-17 manuscript_figures/manuscript_figures.Rmd
Adjust positions of Fig S4 after removing title

ggdraw() +
  draw_plot(pfdr, 0.53, 0.025, 0.24, 0.93) +
  draw_plot(ptpr, 0.77, 0.025, 0.24, 0.93) +
  draw_plot(Fig_impactofinfcov, 0, 0, 0.52, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.53), c(1, 1), size = 15) +
  draw_plot_label("Simulation", 0.71, 0.06, size =11, fontface = "plain")
ggsave(file.path(outdir, "Figure_impactofinfcov_avg_sim.pdf"), width=9.5, height=5)

>>>>

ggdraw() +
  draw_plot(pfdr, 0.53, 0.03, 0.24, 0.97) +
  draw_plot(ptpr, 0.77, 0.03, 0.24, 0.97) +
  draw_plot(Fig_impactofinfcov, 0, 0, 0.52, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.53), c(1, 1), size = 15) +
  draw_plot_label("Simulation", 0.71, 0.06, size =11, fontface = "plain")
ggsave(file.path(outdir, "Figure_impactofinfcov_avg_sim.pdf"), width=9.5, height=5)
